Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-05 manuscript/manuscript.tex
Reorganized "Linear density" in manuscript

For future purposes we are going to obtain the gravity potential for 
three different functions from the perspective of their variation in 
$r'$: a linear and an exponential density function.

@@

\iftwocol{
\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
        Ab 
        \Big[
        & (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1 - \Delta h}{b}} - \\
        & (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2 - \Delta h}{b}}
        \Big].
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}
}{
\begin{equation}
    V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
    Ab \, e^\frac{\Delta h}{b}
    \Big[
    & (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1}{b}} - \\
    & (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2}{b}}
    \Big].
\label{eq:shell-pot-exp}
\end{equation}
}

>>>>

For future purposes we are going to obtain the gravity potential for 
three different functions from the perspective of their variation in 
$r'$: a linear and an exponential density function.
\todo{lo sacaria}

\subsection{Linear Density}

Lets consider a linear density function like:

\begin{equation}
    \rho(r') = ar' + b.
\end{equation}

\noindent The gravitational potential generated by a spherical shell 
with this density on any external point at distance $r$ from its centre 
can be obtained from the following expression:

\noindent The first term on equation \ref{eq:shell-pot-linear} 
reproduces the potential generated by a spherical shell with variable 
density $\rho(r') = ar'$, while the second one constitutes the 
potential generated by a spherical shell with homogeneous density $\rho 
= b$ \citep{Mikuska2006,Grombein2013}. So the potential can be read as 
the one generated by a combination of both shells.

When applying the density-based discretization algorithm on any 
tesseroid with linear density, the absolute difference defined in 
equation \ref{eq:density-abs-diff} will always be zero, so the 
discretization inequation \ref{eq:delta-density} will never be 
satisfied.
Therefore, independently of the linear function proposed, the 
density-based algorithm will never be applied, leaving the modified 
adaptive discretization algorithm as the only mechanism to control the 
accuracy of the numerical approximation.
That's why we only need to determine the minimum value of $D$ needed in 
order to guarantee an acceptable accuracy while ignoring the value of 
$\delta$.

In order to compare the numerical model with the analytical solution we 
must build a spherical shell from a set of tesseroids.
We propose a mesh of $30^\circ \times 30^\circ$ tesseroids to compute 
the gravitational potential, the vertical component of the gradient 
($g_z$) and the diagonal components of the Marussi tensor ($g_{xx}$, 
$g_{yy}$, $g_{zz}$) on four different grids: (1) a grid located at the 
pole, (2) another one on the Equator, (3) one located at satellite 
height and (4) a big grid of $30^\circ \times 30^\circ$.
More information about this grids can be found on Table 
\ref{tab:grids}.

We have computed these gravitational fields on every point of the four 
grids for different values of $D$, ranging from 0.5 to 10 with a step 
of 0.5.
Then we calculated the maximum difference between these results and the 
value that the analytical solution assumes at the same height.
Because the gravity fields generated by a tesseroid are approximated by 
the effect of point masses, the numerical results may vary between 
computation points at same height but at different latitude or 
longitude.
That's why we choose for comparison the maximum difference between the 
results on every point of the grid and the analytical solution.

Finally, we will set the acceptable value of $D$ as the minimum value at which the
corresponding error of the numerical approximation is lower than 0.1\%.

@@

\iftwocol{
\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
        Ab 
        \Big[
        & (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1 - \Delta h}{b}} - \\
        & (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2 - \Delta h}{b}}
        \Big].
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}
}{
\begin{equation}
    V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r} 
    Ab \, e^\frac{\Delta h}{b}
    \Big[
    (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1}{b}} - \\
    (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2}{b}}
    \Big].
\label{eq:shell-pot-exp}
\end{equation}
}
